---
title: "NYSCDraft_III"
author: "Ostinato Rigore"
date: "8 November 2019"
output: 
  word_document: 
    fig_caption: yes
    fig_height: 7.5
    fig_width: 8
    toc: yes
---

```{r setup, include=FALSE}
#echo= False : This makes the codes invincible in the report
#cache = True : Because certain codes had to be constantly remodified & re-run
#, it makes the re-running of the codes chunks quicker
#fig.width = 8: This was an attempt to corce all the charts into a certain dimension.

knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
```

```{r Column names}
#This are the various column namess in the data set this particular variable will be continually used through out the analysis.
##It is necessary to create this from the data.
colnames <- c('LOCATION OF PRIMARY ASSIGNMENT',
              'IN WHICH SECTOR',
              'NATURE OF PLACEMENT',
              'HOW RELEVANT WAS THE FIELD OF STUDY',
              'ASSESSMENT OF ATTITUDE OF PERMANENT STAFF',
              'DEGREE OF JOB SATISFACTION',
              'WERE YOU GIVEN ACCOMMODATION',
              'HOW EFFECTIVE WAS YOUR CDS GROUP',
              'ASSESSMENT OF INTERACTION BETWEEN GROUP MEMBERS TOWARDS THE CDS PROGRAMS',
              'HOW SUPPORTIVE WAS THE HOST COMMUNITY TO THE PROJECT',
              'DO YOU INTEND TO SUSTAIN THE SKILL(S) ACQUIRED',
              'DID YOU HAVE ACCESS TO ANY FINANCIAL SUPPORT',
              'OPINION ABOUT NYSC SCHEME BEFORE MOBILISATION FOR NATIONAL SERVICE',
              'OPINION CHANGE FROM PARTICIPATION IN NYSC',
              'HOW WILL YOU ASSESS DISCIPLINE AMONG CORPS MEMBERS',
              'HOW WILL YOU ASSESS PATRIOTISM',
              'HOW WILL YOU ASSESS THE ADAPTABILITY',
              'HOW WILL YOU ASSESS TEAM SPIRIT',
              'HOW WILL YOU ASSESS THE INTEGRATION',
              'HOW WILL YOU ASSESS  NATIONAL GROWTH',
              'HOW WILL YOU ASSESS SELF RELIANCE',
              'HOW WILL YOU ASSESS NATIONAL UNITY',
              'ARE YOU WILLING TO STAY BACK IN YOUR STATE OFDEPLOYMENT')
```

```{r Importing: Libraries & Dataset, include = FALSE}
#This code chunk, can be divided into the following sections:
##Importing libraries, Note that they have to be downloaded first
##Importing the dataset
##Transforming that dataset into a very nice format called 'tibble', for relevannce it is like turning an image from .png  to .jpeg.

library(tidyverse) 
library(foreign)
library(knitr)


#Importing .sav file from SPSS, use this s/l/a/n/t lines
NYSC2019 <- read.spss('C:/Users/Akanimore/Desktop/NYSC2019/159 QUESTIONNAIRE OUTGOING 2019 CORPERS.sav', 
                      use.value.labels = TRUE, to.data.frame = TRUE, col_names= colnames) 

NYSCtibble <- as_tibble(NYSC2019[-c(195:461),])    #this data ended at row 195, but it exported 461
```

```{r Creating funtions}
#The report is basically categorized into a Table a table, its description, a bar and pie chart, in this code chunk are the functions that we will be re-iterating with through out the analysis.

##This function simply creates a custom proportion of the data set
proportion <-  function(Data) {
  tbl <- table(Data)
  rnd <- ((round(prop.table(tbl), 2) *100)) #Rounds the values to 2, 3 is the std though.
  as.data.frame(rnd)
}

Frequency <- function(Data) {
  as.data.frame(summary(Data))
}

##Uses the kable function from the 'knitr' library to create a table.
Table <- function(Q_No){
  kable(Q_No,
        col.names = c('Frequency', 'Percentage (%)'), 
        align = 'c',
        caption = 'Frequency & Percentage')
}

##Here we create a function that creates charts from the ggplot library.
##Horizontal Bar Charts.
Bar_Chart <- function(Distribution){
  NYSCtibble %>%
  ggplot() +
  geom_bar(aes(x = Distribution, fill = Distribution),
           width = 1) + 
  coord_flip()
}

Pie_Chart <- function(Distribution){
  NYSCtibble %>%
  ggplot() +
  geom_bar(aes(x = Distribution, fill = Distribution),
           width = 1) + 
  coord_polar()
}
```

\newpage

#1 Distribution of `r colnames[1]`  

```{r distribution}
prop <- proportion(NYSCtibble$QB1)

Freq <- Frequency(NYSCtibble$QB1)

Q1 = cbind(Freq, prop[2])

#Using QD3 as e.g.
#a[[1]][1] = YES; [[2]][1] = 0.077
#a[[1]][4] = NA; [[2]][4] = 0.294
```


## Table showing distribution `r colnames[1]` of Corp Members
```{r tabulating}
Table(Q1)
```

The coressponding Table and Chart indicatess that `r Q1[[2]][1]`% were deployed to **`r prop[[1]][1]`**, `r Q1[[2]][2]`% were deployed to **`r prop[[1]][2]`**, while `r Q1[[2]][3]`% of respondents did not respond to the question. 

## Charts showing distribution `r colnames[1]` of Corp Members
```{r charts, fig.weight= 5, fig.height=5}
Bar_Chart(NYSCtibble$QB1)
Pie_Chart(NYSCtibble$QB1)
```
  
\newpage


#2 Distribution of `r colnames[2]`
```{r}
prop <- proportion(NYSCtibble$QB2)

Freq <- Frequency(NYSCtibble$QB2)

Q2 = cbind(Freq, prop[2])

```

## Table showing distribution `r colnames[2]` of Corp Members
```{r }
Table(Q2)
```

Table and Figure below shows that `r Q2[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q2[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, `r Q2[[2]][3]`% were deployed to **`r prop[[1]][3]`** sectors, `r Q2[[2]][4]`% were deployed to **`r prop[[1]][4]`** sectors , while `r Q2[[2]][5]`% of respondents did not respond to the question.

## Charts showing distribution `r colnames[2]` of Corp Members
```{r }
Bar_Chart(NYSCtibble$QB2)
Pie_Chart(NYSCtibble$QB2)
```


\newpage


#3 Distribution of `r colnames[3]`
```{r}
prop <- proportion(NYSCtibble$QB3)

Freq <- Frequency(NYSCtibble$QB3)

Q3 = cbind(Freq, prop[2])
```


## Table showing distribution `r colnames[1]` of Corp Members
```{r}
Table(Q3)
```

The coressponding Table and Chart indicatess that `r Q3[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q3[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, while `r Q3[[2]][3]`% of respondents did not respond to the question. 
  
```{r}
Bar_Chart(NYSCtibble$QB3)
Pie_Chart(NYSCtibble$QB3)
```






\newpage


#4 Distribution of `r colnames[4]`
```{r}
prop <- proportion(NYSCtibble$QB5)

Freq <- Frequency(NYSCtibble$QB5)

Q4 = cbind(Freq, prop[2])
```


## Table showing distribution `r colnames[4]` of Corp Members
```{r}
Table(Q4)
```

The coressponding Table and Chart indicatess that `r Q4[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q4[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, while `r Q4[[2]][3]`% of respondents did not respond to the question. 
  
```{r}
Bar_Chart(NYSCtibble$QB5)
Pie_Chart(NYSCtibble$QB5)
```




\newpage


#5 Distribution of `r colnames[5]`
```{r}
prop <- proportion(NYSCtibble$QB13)

Freq <- Frequency(NYSCtibble$QB13)

Q5 = cbind(Freq, prop[2])
```


## Table showing distribution `r colnames[5]` of Corp Members
```{r}
Table(Q5)
```

The coressponding Table and Chart indicatess that `r Q5[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q5[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, `r Q5[[2]][3]`% were deployed to **`r prop[[1]][3]`** sectors while `r Q4[[2]][4]`% of respondents did not respond to the question. 

## Charts showing distribution `r colnames[5]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QB13)
Pie_Chart(NYSCtibble$QB13)
```

\newpage



#6 Distribution of `r colnames[6]`
```{r}
prop <- proportion(NYSCtibble$QB15)

Freq <- Frequency(NYSCtibble$QB15)

Q6 = cbind(Freq, prop[2])
```


## Table showing distribution `r colnames[5]` of Corp Members
```{r}
Table(Q6)
```

The coressponding Table and Chart indicatess that `r Q6[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q6[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, `r Q6[[2]][3]`% were deployed to **`r prop[[1]][3]`** sectors while `r Q6[[2]][4]`% of respondents did not respond to the question. 

## Charts showing distribution `r colnames[6]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QB15)
Pie_Chart(NYSCtibble$QB15
          
          )
```

\newpage



#7 Distribution of `r colnames[7]`
```{r}
prop <- proportion(NYSCtibble$QB17)

Freq <- Frequency(NYSCtibble$QB17)

Q7 = cbind(Freq, prop[2])
```


## Table showing distribution `r colnames[7]` of Corp Members
```{r}
Table(Q7)
```

The coressponding Table and Chart indicatess that `r Q7[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q7[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, `r Q7[[2]][3]`% were deployed to **`r prop[[1]][3]`** sectors, `r Q7[[2]][4]`% were deployed to **`r prop[[1]][4]`** sectors, `r Q7[[2]][5]`% were deployed to **`r prop[[1]][5]`** sectors, while `r Q7[[2]][6]`% of respondents did not respond to the question. 

## Charts showing distribution `r colnames[7]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QB17)
Pie_Chart(NYSCtibble$QB17)
```

\newpage


#8 Distribution of `r colnames[8]`
```{r}
prop <- proportion(NYSCtibble$QC2)

Freq <- Frequency(NYSCtibble$QC2)

Q8 = cbind(Freq, prop[2])
```


## Table showing distribution `r colnames[8]` of Corp Members
```{r}
Table(Q8)
```

The coressponding Table and Chart indicatess that `r Q8[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q8[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, `r Q8[[2]][3]`% were deployed to **`r prop[[1]][3]`** sectors, while `r Q8[[2]][4]`% of respondents did not respond to the question. 

## Charts showing distribution `r colnames[8]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QC2)
Pie_Chart(NYSCtibble$QC2)
```

\newpage





#9 Distribution of `r colnames[9]`
```{r}
prop <- proportion(NYSCtibble$QC3)

Freq <- Frequency(NYSCtibble$QC3)

Q9 = cbind(Freq, prop[2])
```


## Table showing distribution `r colnames[9]` of Corp Members
```{r}
Table(Q9)
```

The coressponding Table and Chart indicatess that `r Q9[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q9[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, `r Q9[[2]][3]`% were deployed to **`r prop[[1]][3]`** sectors, while `r Q9[[2]][4]`% of respondents did not respond to the question. 

## Charts showing distribution `r colnames[9]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QC3)
Pie_Chart(NYSCtibble$QC3)
```

\newpage





#10 Distribution of `r colnames[10]`
```{r}
prop <- proportion(NYSCtibble$QC8)

Freq <- Frequency(NYSCtibble$QC8)

Q10 = cbind(Freq, prop[2])
```


## Table showing distribution `r colnames[10]` of Corp Members
```{r}
Table(Q10)
```

The coressponding Table and Chart indicatess that `r Q10[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q10[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, `r Q10[[2]][3]`% were deployed to **`r prop[[1]][3]`** sectors, while `r Q10[[2]][4]`% of respondents did not respond to the question. 

## Charts showing distribution `r colnames[10]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QC8)
Pie_Chart(NYSCtibble$QC8)
```

\newpage





#11 Distribution of `r colnames[11]`
```{r}
prop <- proportion(NYSCtibble$QD2)

Freq <- Frequency(NYSCtibble$QD2)

Q11 = cbind(Freq, prop[2])
```


## Table showing distribution `r colnames[11]` of Corp Members
```{r}
Table(Q11)
```

The coressponding Table and Chart indicatess that `r Q11[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q11[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, while `r Q11[[2]][3]`% of respondents did not respond to the question. 

## Charts showing distribution `r colnames[11]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QD2)
Pie_Chart(NYSCtibble$QD2)
```

\newpage




#12 Distribution of `r colnames[12]`
```{r}
prop <- proportion(NYSCtibble$QD3)

Freq <- Frequency(NYSCtibble$QD3)

Q12 = cbind(Freq, prop[2])
```


## Table showing distribution `r colnames[12]` of Corp Members
```{r}
Table(Q12)
```

The coressponding Table and Chart indicatess that `r Q12[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q12[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, while `r Q12[[2]][3]`% of respondents did not respond to the question. 

## Charts showing distribution `r colnames[12]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QD3)
Pie_Chart(NYSCtibble$QD3)
```

\newpage




#13 Distribution of `r colnames[13]`
```{r}
prop <- proportion(NYSCtibble$QE1)

Freq <- Frequency(NYSCtibble$QE1)

Q13 = cbind(Freq, prop[2])
```


## Table showing distribution `r colnames[13]` of Corp Members
```{r}
Table(Q13)
```

The coressponding Table and Chart indicatess that `r Q13[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q13[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, while `r Q13[[2]][3]`% of respondents did not respond to the question. 

## Charts showing distribution `r colnames[13]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QE1)
Pie_Chart(NYSCtibble$QE1)
```

\newpage




#14 Distribution of `r colnames[14]`
```{r}
prop <- proportion(NYSCtibble$QE2)

Freq <- Frequency(NYSCtibble$QE2)

Q14 = cbind(Freq, prop[2])
```


## Table showing distribution `r colnames[14]` of Corp Members
```{r}
Table(Q14)
```

The coressponding Table and Chart indicatess that `r Q14[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q14[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, while `r Q14[[2]][3]`% of respondents did not respond to the question. 

## Charts showing distribution `r colnames[14]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QE2)
Pie_Chart(NYSCtibble$QE2)
```

\newpage





#15 Assessment of Selected NYSC objectives
In this series only certain selected Objectives will be assessed amoung Corp members.

##15.1 Distribution of `r colnames[15]`
```{r}
prop <- proportion(NYSCtibble$QE3a)

Freq <- Frequency(NYSCtibble$QE3a)

Q15 = cbind(Freq, prop[2])
```


### Table showing distribution `r colnames[15]` of Corp Members
```{r}
Table(Q15)
```

The coressponding Table and Chart indicatess that `r Q15[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q15[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, `r Q15[[2]][3]`% were deployed to **`r prop[[1]][3]`** sectors, `r Q15[[2]][4]`% were deployed to **`r prop[[1]][4]`** sectors, while `r Q15[[2]][5]`% of respondents did not respond to the question. 

### Charts showing distribution `r colnames[15]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QE3a)
Pie_Chart(NYSCtibble$QE3a)
```

\newpage




##15.2 Distribution of `r colnames[16]`
```{r}
prop <- proportion(NYSCtibble$QE3b)

Freq <- Frequency(NYSCtibble$QE3b)

Q16 = cbind(Freq, prop[2])
```


### Table showing distribution `r colnames[16]` of Corp Members
```{r}
Table(Q16)
```

The coressponding Table and Chart indicatess that `r Q16[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q16[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, `r Q16[[2]][3]`% were deployed to **`r prop[[1]][3]`** sectors, `r Q16[[2]][4]`% were deployed to **`r prop[[1]][4]`** sectors, while `r Q16[[2]][5]`% of respondents did not respond to the question. 

### Charts showing distribution `r colnames[16]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QE3b)
Pie_Chart(NYSCtibble$QE3b)
```

\newpage




##15.3 Distribution of `r colnames[17]`
```{r}
prop <- proportion(NYSCtibble$QE3c)

Freq <- Frequency(NYSCtibble$QE3c)

Q17 = cbind(Freq, prop[2])
```


### Table showing distribution `r colnames[17]` of Corp Members
```{r}
Table(Q17)
```

The coressponding Table and Chart indicatess that `r Q17[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q17[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, `r Q17[[2]][3]`% were deployed to **`r prop[[1]][3]`** sectors, `r Q17[[2]][4]`% were deployed to **`r prop[[1]][4]`** sectors, while `r Q17[[2]][5]`% of respondents did not respond to the question.

### Charts showing distribution `r colnames[17]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QE3c)
Pie_Chart(NYSCtibble$QE3c)
```

\newpage



##15.4 Distribution of `r colnames[18]`
```{r}
prop <- proportion(NYSCtibble$QE3d)

Freq <- Frequency(NYSCtibble$QE3d)

Q18 = cbind(Freq, prop[2])
```


### Table showing distribution `r colnames[18]` of Corp Members
```{r}
Table(Q18)
```

The coressponding Table and Chart indicatess that `r Q18[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q18[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, `r Q18[[2]][3]`% were deployed to **`r prop[[1]][3]`** sectors, `r Q18[[2]][4]`% were deployed to **`r prop[[1]][4]`** sectors, while `r Q18[[2]][5]`% of respondents did not respond to the question. 

### Charts showing distribution `r colnames[18]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QE3d)
Pie_Chart(NYSCtibble$QE3d)
```

\newpage




##15.5 Distribution of `r colnames[19]`
```{r}
prop <- proportion(NYSCtibble$QE3e)

Freq <- Frequency(NYSCtibble$QE3e)

Q19 = cbind(Freq, prop[2])
```


### Table showing distribution `r colnames[19]` of Corp Members
```{r}
Table(Q19)
```

The coressponding Table and Chart indicatess that `r Q19[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q19[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, `r Q19[[2]][3]`% were deployed to **`r prop[[1]][3]`** sectors, `r Q19[[2]][4]`% were deployed to **`r prop[[1]][4]`** sectors, while `r Q19[[2]][5]`% of respondents did not respond to the question. 

### Charts showing distribution `r colnames[19]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QE3e)
Pie_Chart(NYSCtibble$QE3e)
```

\newpage




##15.6 Distribution of `r colnames[20]`
```{r}
prop <- proportion(NYSCtibble$QE3f)

Freq <- Frequency(NYSCtibble$QE3f)

Q20 = cbind(Freq, prop[2])
```


### Table showing distribution `r colnames[20]` of Corp Members
```{r}
Table(Q20)
```

The coressponding Table and Chart indicatess that `r Q20[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q20[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, `r Q20[[2]][3]`% were deployed to **`r prop[[1]][3]`** sectors, `r Q20[[2]][4]`% were deployed to **`r prop[[1]][4]`** sectors, while `r Q20[[2]][5]`% of respondents did not respond to the question.

### Charts showing distribution `r colnames[20]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QE3f)
Pie_Chart(NYSCtibble$QE3f)
```

\newpage



##15.7 Distribution of `r colnames[21]`
```{r}
prop <- proportion(NYSCtibble$QE3g)

Freq <- Frequency(NYSCtibble$QE3g)

Q21 = cbind(Freq, prop[2])
```


### Table showing distribution `r colnames[21]` of Corp Members
```{r}
Table(Q21)
```

The coressponding Table and Chart indicatess that `r Q21[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q21[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, `r Q21[[2]][3]`% were deployed to **`r prop[[1]][3]`** sectors, `r Q21[[2]][4]`% were deployed to **`r prop[[1]][4]`** sectors, while `r Q21[[2]][5]`% of respondents did not respond to the question. 

### Charts showing distribution `r colnames[21]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QE3g)
Pie_Chart(NYSCtibble$QE3g)
```

\newpage




##15.8 Distribution of `r colnames[22]`
```{r}
prop <- proportion(NYSCtibble$QE3h)

Freq <- Frequency(NYSCtibble$QE3h)

Q22 = cbind(Freq, prop[2])
```


### Table showing distribution `r colnames[22]` of Corp Members
```{r}
Table(Q22)
```

The coressponding Table and Chart indicatess that `r Q22[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q22[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, `r Q22[[2]][3]`% were deployed to **`r prop[[1]][3]`** sectors, `r Q22[[2]][4]`% were deployed to **`r prop[[1]][4]`** sectors, while `r Q22[[2]][5]`% of respondents did not respond to the question. 

### Charts showing distribution `r colnames[22]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QE3h)
Pie_Chart(NYSCtibble$QE3h)
```

\newpage





#16 Distribution of `r colnames[23]`
```{r}
prop <- proportion(NYSCtibble$QE5)

Freq <- Frequency(NYSCtibble$QE5)

Q23 = cbind(Freq, prop[2])
```


## Table showing distribution `r colnames[23]` of Corp Members
```{r}
Table(Q23)
```

The coressponding Table and Chart indicatess that `r Q23[[2]][1]`% were deployed to **`r prop[[1]][1]`** sectors, `r Q23[[2]][2]`% were deployed to **`r prop[[1]][2]`** sectors, while `r Q23[[2]][3]`% of respondents did not respond to the question. 

## Charts showing distribution `r colnames[23]` of Corp Members
```{r}
Bar_Chart(NYSCtibble$QE5)
Pie_Chart(NYSCtibble$QE5)
```